---
title: "Ad Campaign Data Description"
author: "Logan Calder"
date: "December 2, 2015"
output: html_document
---

# Hello
I'd like to get a brief spiel on how advertising campaings are created and
how they work... never know what will be useful. 

I'll start with a description of what the data looks like. I should correct this description as I receive correction. It looks like there is a row in the data for every combination of Campain, Ad Group, Advertised SKU, Keyword, and Start Date. Start Date and End Date seem to always be one day apart. 

If start date and end date are actually defined as described below, then every instance in the data covers a period of 48 hours... (I'm guessing this is bad documentation on Amazon's part, but whoo can say.)

## What Amazon says:
"Use the Campaign Performance Report to view the performance history of your advertising campaigns for the past 60 days.

This report provides insight into the clicks and attributed sales for each campaign, including results for each ad group, SKU and keyword. Knowing how each of your campaigns is performing will allow you to make changes to your keywords and bids to increase the performance of your ads."

Data dictionary: ( from https://sellercentral.amazon.com/gp/help/help-popup.html/ref=spcm_us_camp_camp?itemID=201530720 )

* Campaign Name - The name of your campaign that contains the data being reported.

* Ad Group Name - The name of your ad group that contains the data being reported.

* Advertised SKU - The SKU that was advertised.

* Keyword - The keyword that was used to target your advertised SKU.  NOTE: In campaigns with automatic targeting, the keyword is listed as star.

* Start Date    - This is the first day of your report, starting at 00:00:00 PT (midnight that morning).

* End Date    - This is the last day of your report, ending at 23:59:59 PT (midnight that evening).

* Clicks - Total clicks your ads have received

* Impressions - Total impressions your ads have received. NOTE: Amazon validates click and impression data and removes invalid events generated by robots or spiders. Validation typically occurs within one day. (AND Impressions are the total number of times your advertisement was shown to customers.)

* CTR - Click through rate (clicks รท impressions)

* Total Spend - Total amount you have spent on your ads

* Average CPC - Average cost-per-click paid for your ads

* Currency - This is the currency used to calculate the sales data.

* 1-day Orders Placed (#) - Total orders placed within one day of ad click

* 1-day Ordered Product Sales ($) - Total order value for all SKUs purchased within one day of a click on your ad

* 1-day Conversion Rate - Conversion rate (orders placed รท clicks) for orders that were placed within one day of a click on your ad

* 1-day Same SKU Units Ordered - Total same SKU units ordered within one day of a click on an ad for that same SKU

* 1-day Other SKU Units Ordered - Total other SKU units ordered within one day of a click on an ad for a different SKU

* 1-day Same SKU Units Ordered Product Sales - Total value of same SKUs ordered for orders that occurred within one day of a click on an ad for that same SKU

* 1-day Other SKU Units Ordered Product Sales - Total value of other SKUs ordered for orders that occurred within one day of a click on an ad for a different SKU

* 1-week Orders Placed (#) - Total orders placed within one week of ad click

* 1-week Ordered Product Sales ($) - Total order value for all SKUs purchased within one week of a click on your ad

* 1-week Conversion Rate - Conversion rate (orders placed รท clicks) for orders that were placed within one week of a click on your ad

* 1-week Same SKU Units Ordered - Total same SKU units ordered within one week of a click on an ad for that same SKU

* 1-week Other SKU Units Ordered - Total other SKU units ordered within one week of a click on an ad for a different SKU

* ... it's all pretty much the same... Good to see this though.



```{r}
require(plyr)
load("dataOriginal.RData")
summary(dataOriginal)

llply(dataOriginal, 
      .fun = function(x){
          t = table(x)
          if (is.na(as.numeric(names(t))[1])) {  # that is, if names aren't numbers
              sort(t, dec = T)
          } else {
              t
          }
          
          }
      )
warnings()
```


```{r}
dlply(dataOriginal, 
      .var = .(Advertised.SKU),
      .fun = function(x) x["Campaign.Name", "Ad.Group.Name", "Keyword",
                           "Start.Date", "End.Date", "Clicks", 
                           "Impressions", "Total.Spend", 
                           "X1.day.Ordered.Product.Sales....",
                           "X1.week.Ordered.Product.Sales....",
                           ])
```