% KPI Report
% generated by Logan Calder
% `r as.character(format(Sys.Date(), format="%B %d, %Y"))`



# KPI's by SKU
```{r, include = F}
# Load the necessary SKU KPI data
source("listForKpiReport.R")

input = listForKpiReport()
```


## Top 20%
Here's graphs of the top 20%

```{r echo = F}
input$topSales
input$topItems
````

Here are tables of the top 20%
a row for every time period, a column for every sku, organized alphabetically for the KPI sales
could we do sales and items ordered as a pair?
``` {r, echo = F}
topTableData = input$topSales$data[,c("week", 
                                      "SKU", 
                                      "Units.Ordered", 
                                      "Ordered.Product.Sales")]
```

```{r, results='asis'}
knitr::kable(head(mtcars))  # Makes a table
```


## Bottom 80%
Here are the graphs of the not top 20%

``` {r echo = F, fig.height= 9}
input$bottomSales
```

``` {r echo = F, fig.height= 9}
input$bottomItems
```



# company totals
Thennnnn...
A graph of the daily sales for 56 days

```{r echo = F}
with(input$dailyTotals,
     plot(x = Date,
          y = Ordered.Product.Sales, 
          type = "o", 
          main = "Total daily sales for 56 days",
          ylab = "Daily Sales",
          xlab = "Date"))
```

A graph of the weekly sales for  a year

```{r echo = F}
with(input$weeklyTotals,
     plot(x = Week,
          y = Ordered.Product.Sales, 
          type = "o", 
          main = "Total weekly  sales for 52 weeks",
          ylab = "Weekly Sales",
          xlab = "Week"))
```

And here is the table of KPI's for the company over different time periods

period         | KPI 1         | KPI 2
------------- | ------------- | ---------
Thursday      | Cell 1        | cell 2
7 days        | Cell x        | cell y
14 days       | Cell z        | cell w

## Comparing to last year same time

```{r echo = F}
if(file.exists(
  paste0("lastYearToWeek",weeks[length(weeks)],".csv"))){
source("Read in last year weekly totals.R")  #lastYear
#plot this year
with(input$weeklyTotals,
     plot(Week, Ordered.Product.Sales,
          xlim = c(as.Date("2015-01-01"),max(input$weeklyTotals$Week)),
          ylim = c(0, max(Ordered.Product.Sales)),
          ylab = "weekly sales ($)",
          type = "o",
          lwd = 1.5,
          main = "Weekly Sales, this year vs. last"))
#add last year
with(lastYear,
     points((Week + 365), Ordered.Product.Sales,
     type = "l",
     lty = 6))
}

```



