% KPI Report
% generated by Logan Calder
% `r as.character(format(Sys.Date(), format="%B %d, %Y"))`



## KPI's by SKU
```{r, include = F}
# Load the necessary SKU KPI data
source("listForKpiReport.R")

input = listForKpiReport()
```


### Top 20%
Graphs of the top 20% selling products

```{r echo = F}
input$topSales
input$topItems
````

Here are tables of the top 20%
a row for every time period, a column for every sku, organized alphabetically for the KPI sales
could we do sales and items ordered as a pair?
``` {r, echo = F}
topTableData = input$topSales$data[,c("week", 
                                      "SKU", 
                                      "Units.Ordered", 
                                      "Ordered.Product.Sales")]
```

```{r, results='asis'}
knitr::kable(head(mtcars))  # Makes a table
```


### Bottom 80%
Here are the graphs of the not top 20%

``` {r echo = F, fig.height= 9}
input$bottomSales
```

``` {r echo = F, fig.height= 9}
input$bottomItems
```



## company totals


```{r echo = F}
with(input$dailyTotals,
     plot(x = Date,
          y = Ordered.Product.Sales, 
          type = "o", 
          main = "Total daily sales for 56 days",
          ylab = "Daily Sales",
          xlab = "Date"))
```



```{r echo = F}
with(input$weeklyTotals,
     plot(x = Week,
          y = Ordered.Product.Sales, 
          type = "o", 
          main = "Total weekly  sales for 52 weeks",
          ylab = "Weekly Sales",
          xlab = "Week"))
```

And here is the table of KPI's for the company over different time periods

period         | KPI 1         | KPI 2
------------- | ------------- | ---------
Thursday      | Cell 1        | cell 2
7 days        | Cell x        | cell y
14 days       | Cell z        | cell w


## Cool Stuff

you're featured in logan's portfolio!



```{r map, warning = F,echo = F, eval = F}
require(maps)
old.par <- par()
par(mar = c(0,0,6,0) + .1)
projDir = getwd()
tempDir = "/Users/loganscalder/Google Drive/EliteTechGear/Data/Timeless/Shipment/Processed"
setwd(tempDir)
load("processedShipmentData.RData")

map("state",)
with(processed.shipment.data,
     points(longitude, latitude, pch = 16, col = rgb(0,0,1,.1), cex = .5))
title(main = "Map of orders from May till about now...",
      sub = "Whoa.. I think I can see the Great Salt Lake from here :)
      Pretty cool that people in our home town are buying your stuff")

par(old.par)
setwd(projDir)
```


